---
title: "DSC 200 Lab08 - Importing Data -Term 2232"
date: "`r Sys.Date()`"
output: github_document
---

**Student Name:<insert your name here>**

**Student ID:<insert ID here>**



## Loading Packages

```{r load-packages, message = FALSE}
library(tidyverse)

```


## Tasks

`1. Read in the nobels.csv file from the data/ folder.
```{r}
nobel <- read_csv(file = "data/nobel.csv")
nobel
```
Write your narrative here




`2. Split into two (STEM and non-STEM)

`2.1. Create a new data frame, nobel_stem, that filters for the STEM fields (Physics, Medicine, Chemistry, and Economics).
```{r}

```
Write your narrative below



`2.2. Create another data frame, nobel_nonstem, that filters for the remaining fields.
```{r}

```
Write your narrative here


`3. Write out the two data frames to nobel-stem.csv and nobel-nonstem.csv, respectively, to data/.
```{r}

```
Write your narrative here


`4. Load the sales.xlsx file from the data/ folder, using appropriate arguments for the read_excel() function such that it looks like the output on the left (see lab handout).
```{r}

```
Write your narrative here




`5. Manipulate the sales data to look like the output on the right (see lab handout).
```{r}

```
Write your narrative here




`6. Write out the manipulated data frame to data/sales_last.xlsx to folder.
```{r}

```
Write your narrative here


